### 2025-07-22 paper/sections/other/main_results.qmd
tables added

## Confidence Intervals

@@

## Qualitative Findings for Image Data

@@

>>>>

### Confidence Intervals

@@

### Qualitative Findings for Image Data

@@

### Costs

df = final_table(
    res_dir; 
    ce_var=["distance"], 
    agg_further_vars=[["run", "lambda_energy_eval"]], 
    total_uncertainty=false, 
)
Serialization.serialize("paper/experiments/output/costs.jls", df)
```

::: {#tbl-costs}

```{julia}
#| output: asis
#| eval: true

df = Serialization.deserialize("paper/experiments/output/costs.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)

Costs

### Validity

# Unconstrained:
df = aggregate_ce_evaluation(
    res_dir; 
    ratio=false, 
    rebase=false, 
    y="validity", 
    agg_further_vars=["run", "lambda_energy_eval"], 
    total_uncertainty=false, 
    drop_models=["linear"]
)
df = select(df, Not(:se, :variable)) |> df -> unstack(df, :objective, :mean)
rename!(df, :dataset => :data, :Full => :CT, :Vanilla => :BL)
Serialization.serialize("paper/experiments/output/validity.jls", df)

# Mutability constrained:
df = aggregate_ce_evaluation(
    mtbl_dir; 
    ratio=false, 
    rebase=false, 
    y="validity", 
    agg_further_vars=["run", "lambda_energy_eval"], 
    total_uncertainty=false, 
    drop_models=["linear"]
)
df = select(df, Not(:se, :variable)) |> df -> unstack(df, :objective, :mean)
rename!(df, :dataset => :data, :Full => :CT, :Vanilla => :BL)
Serialization.serialize("paper/experiments/output/validity_mtbl.jls", df)
```

::: {#tbl-val}

```{julia}
#| output: asis
#| eval: true

df = Serialization.deserialize("paper/experiments/output/validity.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)

Validity

::: {#tbl-val-mtbl}

```{julia}
#| output: asis
#| eval: true

df = Serialization.deserialize("paper/experiments/output/validity_mtbl.jls")
inputs = get_table_inputs(df, nothing; backend=Val(:latex))
tabulate_results(
    inputs; 
    table_type=:tabular,
    alignment = [:l, fill(:c, ncol(df)-1)...],
    wrap_table = false,
)

Validity
